Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-23 prop_letter.tex
prop_letter.tex ...
prop_iop.tex \subsection{Quantum $\delta$-deterministic Probability Measures} Added...
prop_letter.tex \section{Kochen-Specker} Merge results from prop_iop.tex

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
\setcounter{secnumdepth}{3}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[1] }
\hyphenation{cryp-to-de-ter-min-is-tic cryp-to-de-ter-min-ism}

@@

For example, assuming the three intervals $\imposs$, $\necess$, and
$\unknown=\left[0,1\right]$, then:
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
\unknown & \text{, otherwise,}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
is a quantum IVPM. This measure represents the beliefs of an
experimenter with no prior knowledge about the particular quantum
system in question; any quantum state would be consistent with
$\bar{\mu}_{1}$ on any projectors. We have that
$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on
$\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
IVPM\nb$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\textrm{ .}
\end{equation}
If we identify the density matrices\nb$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents that an experimenter knows nothing about a coin before
she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
state\nb$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
coin with probability\nb$p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
classical coin should be consistent with the situation where an experimenter
has no prior knowledge.

@@

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
\setcounter{secnumdepth}{3}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[1] }

@@

For example, assuming the three intervals \imposs, \necess, and
$\unknown=\left[0,1\right]$, then:
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
\unknown & \text{, otherwise,}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
is a quantum IVPM. This measure represents the beliefs of an
experimenter with no prior knowledge about the particular quantum
system in question; any quantum state would be consistent with
$\bar{\mu}_{1}$ on any projectors. We have that
$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Restricting $\bar{\mu}_{1}$ on
$\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
IVPM\nb$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\textrm{ .}
\end{equation}
If we identify the density matrices\nb$\proj{0}$ and $\proj{1}$ as
the head and the tail of a coin, respectively, then $\bar{\mu}_{2}$
represents that an experimenter knows nothing about a coin before
she tosses it. Moreover, for each $p\in\left[0,1\right]$, the mixed
state\nb$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
coin with probability\nb$p$ to get head, and $p\proj{0}+\left(1-p\right)\proj{1}$
is consistent with $\bar{\mu}_{2}$ on $\events_{0}$ because any
classical coin should be consistent with the situation where an experimenter
has no prior knowledge.

@@

According to Mermin's comment\nb\cite{Mermin1999},
\begin{quote}
...although the outcomes deduced from such imperfect measurements
will occasionally differ dramatically from those allowed in the ideal
case, if the misalignment is very slight, the statistical distribution
of outcomes will differ only slightly from the ideal case...
\end{quote}
if the imperfection of the measurement is small enough, the finitely
precise measurement should not nullify the Kochen-Specker theorem.
This idea can be modeled precisely by QIVPMs.

\begin{definition}\label{def:delta-deterministic}An interval-valued
probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
is called $\delta$-deterministic if either $\left[\ell,r\right]\subseteq\left[0,\delta\right]$
or $\left[\ell,r\right]\subseteq\left[1-\delta,1\right]$ for every
$\left[\ell,r\right]\in\mathscr{I}$.\end{definition}

For example, any cryptodeterministic QIVPM is $0$-deterministic.
For another example, given a three-dimensional Hilbert space, 
\begin{equation}
\iota_{\infty}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} 
\end{equation}
is a $\frac{1}{3}$-deterministic, where $\iota_{\infty}\left(x\right)=\left[x,x\right]$.
However, we will prove there is no $\delta$-deterministic probability
measures for small $\delta$ due to the Kochen-Specker theorem.

\begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
and a quantum $\delta$-deterministic probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
with $\delta<\left(1+d\right)^{-1}$, then $\mu:\events\rightarrow\left[0,1\right]$
defined by
\begin{equation}
\mu(P)=\begin{cases}
0 & \textrm{if }\bar{\mu}(P)\subseteq\left[0,\delta\right]\textrm{ ;}\\
1 & \textrm{if }\bar{\mu}(P)\subseteq\left[1-\delta,1\right]
\end{cases}
\end{equation}
 is a cryptodeterministic quantum probability measure.\end{lemma}

\begin{proof}~
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have\begin{subequations}
\begin{eqnarray}
 &  & \pmeas\left(P\right)=0\Rightarrow\bar{\mu}(P)\subseteq\left[0,\delta\right]\\
 & \Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
 & \Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
\end{eqnarray}
\end{subequations}Similarly, when $\pmeas\left(P\right)=1$, we also
have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$.
\item Given a collection $\left\{ P_{i}\right\} _{i=1}^{N}$ of pairwise
orthogonal events, we must have $N\le d$. 
\begin{itemize}
\item If $\pmeas(P_{i})=0$ for all $i$, then\begin{subequations}
\begin{eqnarray}
 &  & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[0,N\delta\right]\\
 & \overset{d\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\cap\left[1-\delta,1\right]=\textrm{Ø}\\
 & \Rightarrow & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\left[0,\delta\right]\\
 & \Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=0=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
\end{eqnarray}
\end{subequations}
\item If $\pmeas\left(P_{i_{0}}\right)=1$ for a unique $i_{0}$, then\begin{subequations}
\begin{eqnarray}
 &  & \bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[1-\delta,1\right]\\
 & \Rightarrow & \pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=1=\sum_{i=1}^{N}\pmeas(P_{i})\textrm{ .}
\end{eqnarray}
\end{subequations}
\item If $\pmeas\left(P_{i_{0}}\right)=\pmeas\left(P_{i_{1}}\right)=1$
for $i_{0}\ne i_{1}$, then
\begin{equation}
\bar{\mu}\left(\bigcup_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}(P_{i})\subseteq\left[2-2\delta,N\right]
\end{equation}
which contradicts to definition~\ref{def:delta-deterministic} so
that this case is impossible.
\end{itemize}
\end{itemize}
\end{proof}

Together with the Kochen-Specker theorem, we will have the following
corollary.

\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
probability measure for $\delta<\left(1+d\right)^{-1}$. \end{cor}
